---
title: "p8105_hw3_nk2814"
author: "Naama Kipperman"
date: "10/8/2019"
output: github_document
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

### Problem 1 


Load the Instacart data and necessary packages you might need.
```{r}
library(p8105.datasets)
library(tidyverse)
library("sqldf")
library(dplyr)
data("instacart") 

```

The goal is to do some exploration of this dataset. To that end, write a short description of the dataset, noting the size and structure of the data, describing some key variables, and giving illstrative examples of observations. Then, do or answer the following (commenting on the results of each):

How many aisles are there, and which aisles are the most items ordered from?

There are 134 distinct aisles.
The aisles from which the most items are ordered are 'fresh vegetables', 'fresh fruits', and 'packaged vegetables fruits'.

```{r}

instacart %>% 
  janitor::clean_names() %>% 
  group_by(aisle) %>%
  summarize(
    number_orders=n()
  ) %>% 
  arrange(desc(number_orders))

```

Make a plot that shows the number of items ordered in each aisle, limiting this to aisles with more than 10000 items ordered. Arrange aisles sensibly, and organize your plot so others can read it.

```{r}

instacart %>% 
  janitor::clean_names() %>% 
  group_by(department, aisle) %>% 
  summarize(
    number_orders=n()
  ) %>% 
  arrange(desc(number_orders)) %>% 
  filter(number_orders > 10000) %>% 
  ggplot(aes(x=aisle, y=number_orders, fill=department))+
  geom_col()+
  facet_wrap(~department)
  

```

Make a table showing the three most popular items in each of the aisles “baking ingredients”, “dog food care”, and “packaged vegetables fruits”. Include the number of times each item is ordered in your table.

```{r}
instacart %>% 
  janitor::clean_names() %>% 
  group_by(aisle, product_name) %>% 
  summarize(
    number_orders=n()) %>% 
  arrange(aisle, desc(number_orders)) %>% 
  filter(aisle %in% c("baking ingredients", "dog food care", "packaged vegetables fruits")) %>% 
  top_n(n=3) %>% 
  knitr::kable()
```



